RSA Project Report Paper

### 2016-11-29 Paper/Paper.tex
paper updates

\usepackage{graphicx} % support the \includegraphics command and options
\usepackage{amssymb}

@@

\newcommand{\legendre}[2]{\left(\frac{#1}{#2}\right)}
%%% END Article customizations

@@

\title{RSA Project paper}
\author{\textbf{RSA Group}\\Li Qiu\\Yiwei \\Leester Mei\\Akeem}
%\date{} % Activate to display a given date or no date (if empty),
         % otherwise the current date is printed

@@

@@

Quadratic Sieve method is actually discovered step by step. It is a optimization of Dixon's Factorization Method. So, to learn what is Quadratic Sieve, we have to understand Dixon's Method. And Dixon's Method is also related to Fermat's Factorization and Kraitchik's Factorization Method. Here, I will briefly introduce these three factorization methods.

@@

\subsubsection {Dixon's Factorization}
One of the great improvement of Dixon's method comparing to the method before is that he replace the requirement from ``is a square of an integer'' to ``has only small prime factors''. To explain this we need introduce 2 concepts which are \textbf{Factor Base} and \textbf{Smooth Number}.

@@

\textbf{Smooth Number} is a integer that all its prime factor within the \textbf{Factor Base} which means if we choose integer $B$ and $Q$, $Q = \prod_{i=1}^k{p_i^{a_i}}$ where $a_i, k \in \mathbb{Z}, p_i \in S_{fb}$. We called Q is a \textbf{B-Smooth} Number.

Recall Kraitchik's Method, he suggests to find a relation $y^2 \equiv \left (\prod_{i=1}^k{x_i}\right)^2 \pmod{n}$. But Dixon's idea is different, he is looking for the relation of $\displaystyle y^2 \equiv Q \equiv \prod_{i=1}^k{p_i^{a_i}} \pmod{n}$ where $a_i \in \mathbb{Z},\ k=|S_{fb}|,\ p_i \in S_{fb}$. For each relation is found, it can represent as a exponent vector $\vec{v} = \{a_1, a_2, \dots, a_k\}$ over $\mathbb{F}_{2}$, and after finding $k$ relations, we have a matrix $m = \{\vec{v_i} | i \le k\}$. And searching the null space of this matrix, could help us to find the square integer. Since $M\vec{v} = 0$ where $\vec{v} \in Null\ Space$, we know which rows sum together are equal to 0, which also implies the products of corresponding Q to that row is a square integer. After found the relation, let $x^2 = \prod_i^k{Q_i}$, the factor of n is $gcd(y\pm x, n)$

@@

@@

If we use logarithm approximation, it is very likely to find partial relations instead of full relation. A full relation means the relation is exactly the smooth number. A partial relation means that there are factors out of our factor base. A relation like this is also useful, since we are working over $\mathbb{F}_2$, if we can find another partial relation which have the leftover in common, the leftover will be canceled. In other words, if we can find two partial relations have the same leftover factors we can treat them as two full relations.

@@

\renewcommand\labelenumi{\Roman{enumi}}
\begin{enumerate}
\item \textit{Choosing B \& M:} \vspace{2mm}
\\ We read a lot of resources and most of them suggests a value between $\exp{(\frac{1}{2}\sqrt{\log{n}\log{\log{n}}})}$ and $\exp{(2\sqrt{\log{n}\log{\log{n}}})}$, The reason why choose it this way, an explanation is in the appendix A of Contini's paper \cite{contini}. At first in class professor emphasis that the number is just a toy number, therefore, we are using the smaller bound $\exp{(\frac{1}{2}\sqrt{\log{n}\log{\log{n}}})}$. And then, we use  this bound to test our number, the result is 1.4 million and the factor base size is about 50 thousands. But we use pollard rho found a small factor, and we reduce the original number by dividing this factor which is 809. And we calculate again it became 970000+, and our factor base is shrink to 40 thousands. For the convenience of communication, we choose 1 million as our B.

@@

\item \textit{Building Factor Base:} \vspace{2mm}
\\ To build the factor base, first we need to generate primes. There are several ways to do it. Our approach build a prime generator by Eratosthenes Sieve. we used a dictionary to dynamically hold the relations. For example, if a test number, is not in the dictionary then it is a prime, and then add the square of this number to the dictionary. if the test number in the dictionary, then, pull out all its factors and add the sum of the test number and its factor to the dictionary. after that, delete the test number from the dictionary. Then, we use this generator to build our factor base, if the prime build by generator satisfy two conditions which are less than $B$ and makes $N$ be the quadratic residue, then add it to our factor base, otherwise, continue generating until the prime greater than our $B$. The good part of this method is that the building process is very fast, the cons is that it use extra memory to save the relations.

@@

\item \textit{Sieving:} \vspace{2mm}
\\ The sieving array is to store the accumulated $\log{p}$ value for each position in the range of [$-M, M$]. Therefore, its length is $2M+1$. The sieving process is just go through each prime in our factor base. Get its position which already cached in previous stage, and add $r+ip$ where $r$ is the position to the sieve array.

@@

\subsection {Results of Experiments}

@@

>>>>

\usepackage{graphicx} % support the \includegraphics command and options
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{mathtools}

@@

\newcommand{\itemgap}[1][2]{\vspace{#1mm}}
\newcommand{\legendre}[2]{\left(\frac{#1}{#2}\right)}
%%% END Article customizations

@@

\title{RSA Project Report Paper}
\author{\textbf{RSA Group}\\Li Qiu\\Yiwei \\Leester Mei\\Akeem}
%\date{} % Activate to display a given date or no date (if empty),
         % otherwise the current date is printed

@@

\section{Introduction}
For this assignment, we were given the task of breaking RSA encryption. The data we were given is simply the public key, and the cipher modulus. The problem has specified that the message was encrypted to number format by each being equal to a set of one or two number (Ex: A = 1,B = 2,with Z = 26).

We have the public exponent $ e = 31 $.The public modulus $N=$  49596093737736060492038360\\5744987602701101399399359259262820733407167.
And the cipher text, 19705178523446373241\\426321455642097240677633038639787310457022491789, giving us the full public mechanism in the form $ C \equiv M^{e} $ (mod N)

\indent This is all the information afforded to us to solve the problem of recovering the message. Now we will discuss potential attacks against RSA and the pitfalls of many of them given the information provided.

\subsection{ Common Modulus Attack}
		Assume the same common modulus N is used by all the users under a system, so each user i gets a unique public key pair $<N,e_i>$ and a unique private key pair $<N,d_i>$ from the central system.
		Now, Alice is sending an encrypted message C = $M^{e_{Alice}}$ mod N to Bob (Bob has to know either factors of N or to do the same thing with Eva). 
		However, another user Eve can also get Alice's original message by using her own keys, ${e_{Eve}}$ and ${d_{Eve}}$, to factor common modulus N. There are many ways to factor N if we know e and d.
		For example, we can guess $\phi(n)$  from ed = 1 (mod $\phi(n)$). Since ed -1 = k$\phi(n)$ = k$2^x$r (because $\phi(n)$ must be an even number, $\phi(n)$ can be expressed in powers of 2 times an odd number with a certain integer k),
		we can get correct $\phi(n)$ in $\log_2(N)$.
		Or if we are lucky enough that N = pq, $\phi(n)$ = (p-1)(q-1) = pq - (p+q) +1 = n - (p+q) +1. Then q = (n- $\phi(n)$ +1)-p. By Substituting q into N =pq, N = p(n- $\phi(n)$ +1)-p), which is equal to $p^2$ - p(n-$/phi(n)$+1)+n =0.
		Now we can factor N by solving this quadratic equation.

		After Eve knows the factors of N, she can compute $\phi(N)$ and compute ${d_{Alice}}$ ${e_{Alice}}$ = 1 mod $\phi(N)$ to find ${d_{Alice}}$ by Euclidean algorithm (since ${e_{Alice}}$ is public information).
		Then Eve can recover Alice's M = $C^{d_{Alice}}$ mod N.
		Therefore, common modulus N is not secure.

		However, we are only given one public key $<N,e>$ and there are no other users involving in our case. So, this attack does not apply to our case. 
\subsection{Blinding Attack on RSA signature}
		Assume Alice has a public key pair $<N,e>$ and a private key pair $<N,d>$. Eve asks for Alice to sign a random message M' (M' = $r^eM$ with r picked by Eve randomly and M is the targeted high secret message).
		Then, by the fact that signature S' = $M'^d$ mod N and S = s'/r, Eve can recover M by computing $S'^e/r^e$ since $S^e$ = $(S')^e/r^e$ = $(M')^ed / r^e$ = $M'/r^e$ = M mod N.

		Our problem doesn't involve in digital signature.
\subsection{Small private Exponent Attack}

		1. d has to be large enough to be secure (drawback: large d would take more computation time and a large storage space for smart cards)

		2. d can be recovered in linear time if d is small
		it does not apply to our case because we don't have information about d so that it would be inefficient to apply this attack.

\subsection{ Small public Exponent Attack}
		Sometimes it is possible that we use small small public exponent in order to reduce encryption time. However, it is not secure and we show several methods to break RSA by having small public exponent as following.

\subsubsection{Hastad's Broadcast Attack}
		Assume Alice wants to send a message to many users (k of them). It is possible that Alice is lazy to compute $M^(e_i)$ according to each user, so she may choose the same e for all users.
		Then She first encrypts the message M according to a user's public key pair $<N_i, e>$ by $M^e$ (mod $N_i$) = $C_i$ and sends the cipher text $C_i$ to the corresponding user i. 
		If Eve can intercept k cipher text, she can recover the encrypted message as following.
		She first take congruence of each user's cipher text to get $(M_i)^k$ by $C_i$ = $(M_i)^k$ (mod $N_i$). Then she applies the Chinese Remainder Theorem to each $C_i$, which gives C' = $M^k$ (mod ($N_1$)*($N_2$)*...*($N_k$)).
		Since M is less than all $N_i$, $M^k$ < ($N_1$)*($N_2$)*...*($N_k$) is satisfied, which means C' = $M^k$. So, Eve can recover M by taking k root of C'.
		This attack is efficient only when e is the same for all users and e is small.

		It does not apply to our case because it has to send message to many people. In our case, Alice only send message to Bob so we only have one public key pair $<N, e>$. Thus, we cannot recover M by using Chinese Remainder Theorem.

\subsubsection{Franklin-Reiter Related Message Attack}

		it does not apply to our case because it has to send related messages using same modulus N. In our case, we only intercept one message.

\subsection{implementation attacks}
	it does not apply to our case because it needs to measure the time it takes for decryption. In our case, we do not have such information.

\section{Factoring Attacks Against RSA}
\subsection{Special Factoring Methods}
		The efficiency of this type of methods usually depends on the size of the first prime factor or some special form of N. If the first prime factor is small (N is less than 100 bits) or N can be expressed in some special forms, these methods can find the first prime factor fast.
		Thus, we usually apply these special factoring methods to find whether there is a small prime factor to divide N so that we can decrease the size of N before proceed with the general factoring methods.

 \subsubsection{ Brute Force}
		The brute force method we used here is to do the trial division from 2 and 3 to $\sqrt{N}$ and increase by 2.
		In this month, we search up to 58248674129 (35-bit), which is 21 digits difference with the second prime factor 64820903298591432157114065708311(105-bit).
		And it will take us 7.6*$10^{18}$ years to reach the second prime factor if we use brute force search.
		Moreover, the completely search from 1 to N will take about 5*$10^{55}$ years. (all the calculations above are done by Java) 
		Therefore, if we only use brute force search to factor N, we won't be able to reach the solution until 7.6*$10^{16}$ generations after (and each generation should continue this task non-stop).

 \subsubsection{Pollard's Rho method}
		Assume we want to factor a positive number N. We begin by randomly selecting with replacement from the set $S_1$ = {0,1,2,...,N-1} to form a sequence $x_1$, $x_2$, $x_3$,.... 
		Define $x_i$' = $x_i$ mod p so that our sequence is now $x_1$', $x_2$',$x_3$',... with each $x_i$' belongs to $S_2$ = {0,1,2,...,p-1}.
		Because the sets $S_1$,$S_2$ are finite, eventually there will be a repeated integer in both sequence. Say, $x_i$' = $x_j$' for i $\ne$ j. Then, $x_i$ $\equiv$ $x_j$ mod p, which means p$|$($x_i$ - $x_j$) if $x_i$ is not equal to $x_j$.
		So, gcd($|$$x_i$ - $x_j$$|$, N) $\ne$ 1. Then if, gcd($|$$x_i$ - $x_j$$|$, N) $\ne$ N, we have found a proper divisor for N.

		In our case, we factor 495960937377360604920383605744987602701101399399359259262820\\733407167 = 809*613054310726032886180943888436325837702226698886723435429939101863 using Pollard's rho algorithm within 6 ms by Java.
		And after using Miller-Rabin's primality test, we found that 613054310726032886180943888436325837702226698886723435429939101863 is a composite number.
		So, we keep factoring 61305431072603288618094388843632583770222669888\\672435429939101863 using Pollard's rho algorithm.
		However, the Pollard's rho algorithm program is still running, so we failed to use this algorithm to factor N in one month.
\subsubsection{Pollard's P-1}
By Fermat’s Little Theorem, if $a$ and $p$ are coprime, then $a^{p-1} = 1(mod\ p)$, which means that $a^{k(p-1)} (mod\ p)$ should also be $1$. Say $p$ and $q$ are prime factors of the number we want to factor, $N$. If we can find an integer $L$, such that $p-1| L$, meaning $k(p-1) = L$ for some integer $k$ and $a^{L} = 1(mod p)$, we then know that $p|a^{L-1}$. From there we can calculate gcd($a^{L-1}$, $N$), which we can have two cases. The first case is if the gcd($a^{L-1}$, $N$) is not equal to $N$, which means that the gcd must be our prime factor p (since $a^{L-1} = kp$, for some integer $k$, $N = pq$, and gcd($kp$, $pq$) = $p$). The second case is if gcd($a^{L-1}$, $N$) = $N$, which implies that $N| a^{L-1}$. In this case $q$ will also divide $a^{L-1}$, meaning $a^{L} = 1(mod q)$ (because $a^{L-1} = 0(mod q)$).
\\\\Algorithm
	\\1. Choose $a$, where $1<a<n$
	\\2. Check if gcd($a$,$n$) != 1, if it is, (though not likely), then you’ve found a factor, $a$.
	\\3. Otherwise, for $r$ = $2,3,..$ compute the gcd($a^{r!-1}$, $n$) = $d$:
	\\If $d = n$, then go back to (1), try a different a
	\\If $d \ne n$, but $d > 1$,  then $d$ is a prime factor of 
	\\Otherwise, if $d = 1$, increment $r$ and repeat
\\\\
Note: We use $r!$ as our exponent since $r!$ will have a lot of small prime factors, but we can also have a bound $B$, and take the product of all primes < $B$ as well, with an increasing $B$ instead of $r!$. The goal is to find an $L$ such that it is a large multiple of $p-1$
\\\\An attempt at factoring our $N$ using Pollard’s $p-1$ factoring algorithm also proved to yield similar results with Pollard rho factorization. The algorithm itself, which relies on $p-1$, where $p$ is a prime factor of $N$ containing a lot of small prime factors, fails to further factor $N$ beyond the initial 809 factor.

\subsection{William's P+1}
Now we will be discussing our attempt at factoring our modulus using the Williams P+1 method of factoring. This method was based on one of the steps in the P-1 algorithm, and it's effectiveness is determinant on whether p+1 where p is a prime divisor of the number to be factored is a smooth number (Smooth numbers will be discussed in-depth in the section about the quadratic sieve). For this section the explanation of the method will come primarily from Williams paper from 1982 "A P+1 Method of Factoring" and then a discussion of the implementation and the result of this method against both the project modulus and the modulus with 809 factored out.

\indent As stated earlier the P+1 method is based on one of the steps of the P-1 algorithm. The specific step that is talked about is the first step of the algorithm. The specific step will be William's referred to will be reiterated here drawn mostly from his 1982 paper. Let a prime factor of a composite number N have the property that $p = (\prod^{k}_{i=1}q^{a_i})+1$ where $q_i$ is the ith prime and $q^{\alpha_i}_i\leq B_i$. $q^{\beta}_i$ will now be a power of $q_i$  with $q^{\beta}_i \leq B_1$ and $q^{\beta+1}_i > B_1$. Now we allow a value R to be defined as $R= \prod^{k}_{i=1}q^{\beta _i}_i$. With this in mind a few additional facts appear. Firstly $p-1|R$ and due Fermat's Little Theorem  $a^{p-1} \equiv 1$ (mod p) and $a^{R} \equiv 1$ (mod p) when a is a constant which is co-prime to N. The result of these statements is that $p|(N,a^{R}-1)$. This step is the basis of the P+1 method, which utilizes Lucas functions.

\indent A Lucas sequence is a recurrence relation that satisfies of $x^2 - Px+Q$ where with P and Q being integers.In the paper there are seven different identities for Lucas sequences described.These identities stem from this first equation (which is noted by the paper to be the formal definition of a Lucas Sequence)  $U_n(P,Q) = (\alpha^{n}-\beta^{n})/(\alpha-\beta), V_n(P,Q) = \alpha^{n}+\beta^{n}$ where $\alpha$ and $\beta$  are the roots of $x^{}2 - Px+Q$. All the identities won't be outlined here, however there are multiple identities used in the algorithm for the P+1 method. 
\\\\
\indent The algorithm itself as outlined in the paper is similar to the following. Let $p = (\prod^{k}_{i=1}q^{\alpha_i}_i - 1)$ where p is a prime factor of N. If we define R in the same way as in the P-1 method then $p+1|R$ and $p|U_R(P,Q)$ thus $p|(U_R(P,Q),N)$. The issues with this method is the calculation of $U_R$ which can be a very large number as the size of R may be very large. A method is described to get around this which ends in an assumption that Q may be set to be equal to one in the calculations of all Lucas sequences involved in this algorithm. 
\\\\
\indent There is a second bypass involved to decrease the computational load that leads to the primary implementation done for our assignment. The details to this implementation are outlined in the paper itself. This method was implemented on a laptop computer with a I3 Intel processor that clocks at 2.2 Gigahertz with a RAM size of 4.0 gigabytes. Firstly define a Lucas Sequence to be $V_n = V_{n-1}+V{n_2}$ where $V_0 = 2$ and $V_1 = a$ with a being an integer larger than 2. Then create a loop that continuously calculates $V_{n!}$ where $n \geq 2$. Then after every iteration of this loop calculate the GCD of (N,$V_{n!}-2$) this was done using the Euclid's Algorithm. When the GCD is not equal to either 1 or N, then you have a non trivial factor of N. The major difficulty of implementing this algorithm was the computational overload of calculating subsequent factorial Lucas Sequences. There was a small work around to this to relieve some of the burden of this by recognizing that $V_{n!}(a) = V_n({V_{n-1}})$ meaning if we allow the input to the Lucas sequence to be the output to the previous Lucas Sequence, we can get the factorials of the initial input a without having to actually calculate subsequent factorials of that Lucas Sequence. Without this work around even five iterations of this loop quickly became lengthy to calculate, as it would be $V_120$, an extreme amount of stack calls on the limited hardware being used. The numbers still become prohibitively large for the hardware fairly quickly, in about 15 iterations. So a limit on the number of iterations was engraved in the method (about 15 or so). The paper itself mentions in the implementation and results section that the P+1 method was about 9 times slower than the P-1 method possibly likely due to the calculation of a Lucas sequence on top of the calculation of the factorial that the P-1 method already had. When actually run on the original modulus the algorithm once again found 809 to be a factor about 5 seconds. Use of the method on the modulus with 809 divided out produced no further results, even when run for over 20+ hours. At this time an estimate for the time the program would actually factor the second modulus has not been produced. The only new information that could be extrapolated from this would be that the probability of the p+1 of the larger number being comprised of mostly small factors would be low provided that the premise of the algorithm itself is to be believed. This ends the discussion of William's P+1 method and our attempt to implement it for our assignment.

\section{The Quadratic Sieve}
At last we come to the crux of our assignment, The Quadratic Sieve. The quadratic sieve is faster for numbers under 100 digits\cite{pomerance}. This method was invented by Carl Pomerance in 1981 after a series of enhancements on Fermat's factoring method led to the idea of utilizing smooth numbers to set up a matrix to with enough vectors of which to assure that the squares need for Fermat's method would be found. We decided within the first two weeks to stick to the Quadratic Sieve over other methods after we exhausted all the other options listed above.
\\\\
Firstly we will discuss the Quadratic Sieve in detail, explaining what the algorithm is and how it works (similar to the above sections but tackling it in depth). Then we will explain our journey through the implementation of the Quadratic Sieve, our problems as well as the solutions to those problems. Then we will finally discuss the final results to this assignment.
\subsection{Basic's of the Algorithm}

\subsection{Application of Linear Algebra}
\indent For In this section we will talk about the input of Linear Algebra for this algorithm. All information in this section not within "A Tale of Two Sieves" will be otherwise sourced. Linear Algebra is a key component to the quadratic Sieve Algorithm and is the tool used to actually identify the numbers that would be factors out of all the potential candidates found in the data collection/Sieving phase. This component of the Quadratic Sieve method was created when John Brillheart and Michael Morris Utilization multiple linear algebra concepts we convert the smooth numbers found in the earlier stages of the algorithm into exponent vectors. As in a vector of the exponents of a numbers prime factors. This vector shall be converted into a vector in a finite field of size 2 ($F_2$). This is due to the fact that a number is a square if and only if all of it's prime factors exponents add up to zero. Thus there is no need to have the vectors number be out of $F_2$. The objective of having these vectors is to create a matrix of theses exponent vectors. The size of the matrix will be the size of our factor base cross the size of our factor base plus at least 1,(so if $F_B = p_0p_1\dots p_i$ we will have a matrix of size $(ixi)+1$) With this matrix we will use a few properties of linear algebra to find which combination of smooth numbers will give us our factorization. 
\\\\
\indent So firstly, why do we add the vectors? This is because adding the vectors is the equivalent of multiplying the integers themselves in terms of determining if the product of those two numbers (or more) will be a square. As an example consider the integers $24 = 2^{3}*3^{1}$ and $15 = 3^{1}*5^{1} $ The exponent vectors for these two will be 110 and 011 the sum vector of these two numbers is not zero and hence the multiple of 24 and 15 is not a square. Secondly the reasoning to having one more vector than the size of the factor is due to a linear algebra concept known as Linear dependence. Linear dependence tells us that when the number of vectors(rows) exceed the number of dimensions (columns), the sum of a subset of the vectors must be equal to zero. Now finding the subset of vectors that equal to zero can be computationally difficult if the matrix became large enough (if you simply try all the combinations ), however there is a technique within Linear Algebra called Gaussian Elimination that can greatly decrease the complexity of finding the zero subset (discussed more in the implementation section). Thus by ensuring that the amount of smooth numbers collected exceeds the factor base guarantees that we obtain a square within the resulting matrix. Obtaining a factor from the square is not guaranteed however, as half of the possible squares will yield an uninteresting solution. So even with the convenience of the matrix there is some luck involved.

@@

Quadratic Sieve method is actually built upon previous factorization method. It is a optimization of Dixon's Factorization Method. So, to learn what is Quadratic Sieve, we have to understand Dixon's Method first, which is also related to Fermat's Factorization and Kraitchik's Factorization Method. Here, we will briefly introduce these three factorization methods.

@@

\subsubsection {Dixon's Factorization}
One of the great improvement of Dixon's method compared to the previous methods is that he replaces the requirement from ``is a square of an integer'' to ``has only small prime factors''. To explain this, we need introduce two concepts which are \textbf{Factor Base} and \textbf{Smooth Number}.

@@

\textbf{Smooth Number} is an integer in which all its prime factors are within the \textbf{Factor Base} which means if we choose integer $B$ and $Q$, $Q = \prod_{i=1}^k{p_i^{a_i}}$ where $a_i, k \in \mathbb{Z}, p_i \in S_{fb}$. We called Q is a \textbf{B-Smooth} Number.

Recall Kraitchik's Method, he suggests to find a relation $y^2 \equiv \left (\prod_{i=1}^k{x_i}\right)^2 \pmod{n}$. But Dixon's idea is different, he is looking for the relation of $\displaystyle y^2 \equiv Q \equiv \prod_{i=1}^k{p_i^{a_i}} \pmod{n}$ where $a_i \in \mathbb{Z},\ k=|S_{fb}|,\ p_i \in S_{fb}$. For each relation  found, it can be represented as an exponent vector $\vec{v} = \{a_1, a_2, \dots, a_k\}$ over $\mathbb{F}_{2}$, and after finding $k$ relations, we have a matrix $m = \{\vec{v_i} | i \le k\}$. And searching the null space of this matrix could help us to find the square integer. Since $M\vec{v} = \vec{0}$ where $\vec{v} \in Null\ Space$, we know which rows sum together are equal to $\vec{0}$, which also implies the products of corresponding Q to that row is a square integer. After we find the relations, let $x^2 = \prod_i^k{Q_i}$, the factor of n is $gcd(y\pm x, n)$

@@

Once again, like in previous factoring methods such as in Fermat’s or Dixon’s, we rely on finding two integers, $x$ and $y$,such that N can be expressed as the difference of two squares, $x^{2}-y^{2}$. From there we can apply simply algebra find the two factors of $N$, $(x-y)$ and $(x+y)$. This may seem simply enough, but how exactly do you find such $x$ and $y$? Surely we could try to check every integer $x$, from $sqrt{N}$ to $N$ and see if $x^{2}-N$ is a square or not, like in Fermat’s, but this method is too slow for large numbers of $N$. For small numbers of $N$, trial division would work fine. We, however, don’t need to search the entire interval to find a square. Take for example the number $N = 1649$. The
 $\sqrt{1649} = 41$ so we can begin being to find squares starting with 41.  We have\\
 $41^{2} = 32 = 2^{5}$ \\ $42^{2} = 115 = 5\cdot 23$ \\ $42^{3} = 200 = 2^{3}\cdot 5^{2}$ mod $N$, and so on.
 \\\\Note that none of these numbers individually produce a square, but \\$41^{2}\cdot43^{2}\equiv 2^{5}\cdot2^{3}\cdot5^{2}\equiv 2^{8}\cdot5^{2}\equiv (2^{4}\cdot 5)^{2}$ produces a square. 
 Additionally, even after finding such a and b, we must check if the result is ‘interesting’. According to Pomerance, there are “surely plenty of uninteresting pairs $a$,$b$, with $a^{2}-b^{2}(mod  n)$..namely take any value of $a$ and let $b = \pm a$”. 
 However, if we were to instead find an $a$ and $b$ such that $a^{2}\equiv b^{2}(mod N)$, and $b \not\equiv \pm a(mod N)$ then we have found an interesting pair, which would lead to a nontrivial factorization of $N$, through taking the gcd($a\pm b$,$n$). This is because although N divides $a^{2}-b^{2}\equiv(a-b)(a+b)$, N does not divide either $(a-b)$ or $(a+b)$ individually because of the second condition. Hence non trivial factors $(a-b, N)$ and $(a+b, N)$. 
\\\\
So instead of searching through the entire interval from $sqrt{N}$ to N looking for an individual integer a, such that $a^{2} - N = b^{2}$, we can find a subsequence of integers, such that the product will yield a square as well. But how exactly do you find such a subsequence? Surely we cannot examine all subsequences, for given an interval of length L, there would be $2^{L}$ possible subsequences, in other words, an exponential growth in the number of subsequences as L gets bigger. Furthermore, how long of a sequence do we need to examine before we find such a subsequence, and how do we know what the subsequence is? 
\\Well, Pomerance provides us with this lemma:
\\\\LEMMA. If $m_1$,$m_2$,...$m_k$ are positive B-smooth integers, and if $k > \pi(B)$ (where $\pi{B})$ denotes the number of primes in the interval $[1, B]$, then some non-empty subsequence of ($m_i$) has a product of a square. (Pomerance)
\\\\Recall the definition of B-smooth numbers, where a number is B-smooth if all factors in the prime factorization of said number are less than B. Pomerance observes that if a number in the sequence is not B-smooth, than it is unlikely that it will be used in our subsequence. This is in observance of the fact that if a number is not B-smooth, the number contains a prime larger than B, and if we were to use this number in our subsequence, there must be one other number which also contains that prime. However, if such a prime were large, finding another number with such a prime factor will not be easy, hence why we need some bound B. 
\\Essentially, Pomerance’s lemma states that if we were to find at least $\pi{B}$ B-smooth numbers, we are able to find some subsequence of those numbers that would be a product of a square. So say we have a sequence of numbers $m_1$,$m_2$,...$m_k$, where $k>\pi{B}$, we can represent each $m_i$ as a product of those primes less than $B$, namely $p_1$,$p_2$,...$p_j$. From here we are only interesting in a subsequence of $m_i$’s where there product is a square, but how do we go about finding it? Well, by applying some linear algebra, we can represent each number as an exponent vector of length $j$, the length of our factor base, where each entry in the vector corresponds to the exponent corresponding to the same prime in the prime factorization of $m_i$.For example, given a factor base of \{2,3,5,7\}, the exponent vector of the number 336 would just be [4, 1, 0, 1]. 
\\\\ Additionally, we want to work with numbers in GF(2), since we are only interested whether or not some combination will yield even exponents, represented as 0 for even exponent and 1 for odd exponent in our vector, because ultimately we want some subsequence whose product is a square, which means each exponent will be a multiple of 2. After creating such a $k$ by $j$ matrix, we want to find some number of rows who when combined together form a vector of 0's, the zero vector of length $j$, which is why we need to calculate the null space of the matrix. Put simply, the null space of a matrix is the set of all vectors, $v$, such that given a matrix $A$, the product $A\cdot v$, yields the zero vector, which is exactly what we want. In our case the null space will yield vectors, each vector containing only entries of 1s and 0s, in which every 1 corresponds to a row in which that $m_i$ belongs to our subsequence. 
\\\\Another problem that arises, however, is selecting such a bound B. What exactly is a good limit for the bound B? 
\\How do we populate the factor base given a bound B? Perhaps it may seem necessary to store a large number of primes in order to sieve, but in fact we can easily generate all primes less than B through applying the Sieve of Eratosthenes:
\\\\Algorithm: We start with a table of numbers (e.g., 2, 3, 4, 5, . . . ) and progressively cross off numbers in the table until the only numbers left are primes. Specifically, we begin with the first number, p, in the table, and 
\\1. Declare p to be prime, and cross off all the multiples of that number in the table, starting from $p^{2}$;
\\2. Find the next number in the table after p that is not yet crossed off and set p to that number; and then repeat from step 1. (O’Niel)
\\\\Now, the problem is, how do we find the necessary amount of B-smooth numbers needed to factor N? Surely, a naive approach would be to trial divide a number by the primes in the factor base until you either get a 1, in which case the number is B-smooth, or you get a number larger larger than B which is not a multiple of any prime in the factor base, in which case it’s not B-smooth. Indeed, this approach would be much too slow, given a sufficiently large bound B, B-smooth numbers are far and few between. It would be a huge waste of time and resources. 
\\A further improvement could be to only consider numbers which are multiples of primes in the factor base. Say in our interval $[\sqrt{N},N]$ and a prime in our factor base, p, we notice that at some point, x, the number $x^{2}-N$ will be a multiple of p, which can be represented as $\sqrt{N}+i$, where i is the distance from the start of the interval. From there, every subsequent multiple of p is $k*i$ distance away from $\sqrt{N}$. Essentially we will have to solve for $x$ in $x^{2}-N\equiv 0(mod p_i)$, which can yield either 2, 1 or 0 solutions. We can do this for every $p_i$ in the factor base and ‘mark’ numbers that are multiples of said prime. Then, we will only check marked numbers in our interval by dividing only those primes that marked the number, hence not having to check every number in the interval, and not having to trial divide by every prime in the factor base. In the end, this method will work, but does not scale well (as in our case), which is further explained in Sect. 4.5.
\\\\
Additionally, with a defined bound B, should we consider all the primes less than B? Recall the definition of a quadratic residue:
\\\\
Definition: An integer q is called a quadratic residue mod n, if it is congruent to a perfect square mod n. In other words, there exists an x such that, $x^{2} \equiv q(mod n)$ 
\\\\
When we attempt to sieve, we try to calculate $x^{2}-N\equiv 0(mod p_i)$ where $p_i$ a prime from the factor base, which can be rewritten as $x^{2} \equiv N(mod p_i)$. Does this seem familiar? Well this essentially boils down to finding out whether or not N is a quadratic residue of $p_i$, in other words, are there solutions, $x$, such that $x^{2}\equiv N(mod p_i)$. In effect, not all primes less than $B$ should be in our factor base. More specifically, only those primes, $p_i$, less than $B$ such that $N$ is a quadratic residue modulo $p_i$, should be added to our factor base. 
\\Now the obvious question arises: how do you know if N is a quadratic residue modulo p? Recall the definition of the legendre symbol:
\\\\
Definition: The legendre symbol of a and p where p is an odd prime is defined as 
\\\\
$\frac{a}{p} = $
\\$1$ if a is a quadratic residue modulo p and $a\not\equiv 0(mod p)$
\\$-1$ if a is quadratic non-residue modulo p
\\$0$ if $a\equiv 0(mod p)$
\\\\Additionally we will introduce the Law of Quadratic Reciprocity:
\\\\
Definition: If p and q are distinct odd primes then:
\\(a)$(\frac{p}{q})(\frac{q}{p}) = (-1)^{\frac{(p-1)(q-1)}{4}}$
\\(b)$\frac{1}{p} = 1$
\\(c)$(\frac{-1}{p}) = (-1)^{\frac{p-1}{2}}$
\\(d)$(\frac{2}{p} = (-1)^{\frac{p^{2}-1}{8}})$
\\\\
Through applying the Law of Quadratic Reciprocity, it is trivial to calculate $\frac{N}{p_i}$ to find which primes will make N a quadratic residue.

@@

If we use logarithm approximation, it is very likely to find partial relations instead of full relation. A full relation means the relation is exactly the smooth number. A partial relation means that there are factors out of our factor base. A relation like this is also useful, since we are working over $\mathbb{F}_2$, if we can find another partial relation which have the leftover in common, the leftover will be canceled. In other words, if we can find two partial relations have the same leftover factors we can treat them as one full relation.

@@

\renewcommand\labelenumi{\Roman{enumi}}
\begin{enumerate}
\item \textit{Choosing B \& M:} \itemgap
\\ We read a lot of resources and most of them suggests a value between $\exp{(\frac{1}{2}\sqrt{\log{n}\log{\log{n}}})}$ and $\exp{(2\sqrt{\log{n}\log{\log{n}}})}$, The reason why choose it this way, an explanation is in the appendix A of Contini's paper \cite{contini}. At first in class professor emphasis that the number is just a toy number, therefore, we are using the smaller bound $\exp{(\frac{1}{2}\sqrt{\log{n}\log{\log{n}}})}$. And then, we use  this bound to test our number, the result is 1.4 million and the factor base size is about 50 thousands. But we use pollard rho found a small factor, and we reduce the original number by dividing this factor which is 809. And we calculate again it became 970000+, and our factor base is shrink to 40 thousands. For the convenience of communication, we choose 1 million as our B.

@@

\item \textit{Building Factor Base:} \itemgap
\\ To build the factor base, first we need to generate primes. There are several ways to do it. Our approach build a prime generator by Eratosthenes Sieve. we used a dictionary to dynamically hold the relations. For example, if a test number, is not in the dictionary then it is a prime, and then add the square of this number to the dictionary. if the test number in the dictionary, then, pull out all its factors and add the sum of the test number and its factor to the dictionary. after that, delete the test number from the dictionary. Then, we use this generator to build our factor base, if the prime build by generator satisfy two conditions which are less than $B$ and makes $N$ be the quadratic residue, then add it to our factor base, otherwise, continue generating until the prime greater than our $B$. The good part of this method is that the building process is very fast, the cons is that it use extra memory to save the relations.

@@

\item \textit{Sieving:} \itemgap
\\ The sieving array is to store the accumulated $\log{p}$ value for each position in the range of [$-M, M$]. Therefore, its length is $2M+1$. The sieving process is just go through each prime in our factor base. Get its position which already cached in previous stage, and add $r+ip$ where $r$ is the position to the sieve array.

@@

@@

\bibitem{silverman} Robert D. Silverman, [\textit{The Multiple Polynomial Quadratic Sieve}], Mathematics of Computation, Volume 48, Issue 177(Jan., 1987), 329-339.
